---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# codeusage: Code Usage in England 

<!-- badges: start -->

[![R-CMD-check](https://github.com/ebmdatalab/codeusage/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ebmdatalab/codeusage/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `codeusage` is to make yearly summaries of **SNOMED Code Usage in Primary Care** published by NHS Digital available in R for research. 
The original data is available from NHS Digital at:

- [SNOMED Code Usage in Primary Care](https://digital.nhs.uk/data-and-information/publications/statistical/mi-snomed-code-usage-in-primary-care)

## Installation

You can install the development version of `codeusage` like so:

```r
remotes::install_github("ebmdatalab/codeusage")
```

## Example

```{r load-pkg}
# Load codeusage package
library(codeusage)
```

### Dataset: SNOMED Code Usage in Primary Care in England

This is only a selection of the full dataset published by NHS Digital, for the data pre-processing see
`/data-raw/snomed_code_usage.R`.

```{r snomed-usage}
# Return SNOMED code usage data
snomed_usage
```
